Poker Chips, Earthquakes, and Computation

### 2014-10-13 finaldraft.tex
fixed more typos

In fact we are able to show that not only is this final board the same but that the number of earthquakes that target a particular node in order to stabilize the board is invariant of the order in which the earthquakes occur. We show this by first describing conditions under which we can rearrange a sequence earthquakes without changing the resultant board. We then define a process that rearranges a sequence of earthquakes without changing the final board state and for a given board will always produce the same sequence.\\

@@

\begin{definition}
We say that an earthquake $E$ is valid if the node it targets has at least $4$ chips on it. 
We say that a sequence of earthquakes $E_1, E_2, \ldots E_n$ to be a valid sequence of earthquakes if each earthquake is valid when applied one after another. 
\end{definition}

@@

We prove this by contradiction. Assume $E_2, E_1$ is an invalid sequence, that is $E_2 b(s_1)<4$. Since $E_1$ is a valid earthquake when applied directly to $b$, we know $b(s_1) \geq 4 $. 
Therefore we must have $b(s_1)<8$ and $s_2=s_1$. But then $E_1 b(s_1)<4$ and so $E_1, E_2$ would not be a valid sequence of earthquakes. This contradicts one our hypothesis and so $E_2, E_1$ is a valid sequence.

>>>>

In fact we are able to show that not only is this final board the same but that the number of earthquakes that target a particular node in order to stabilize the board is invariant of the order in which the earthquakes occur. We show this by first describing conditions under which we can rearrange a sequence of earthquakes without changing the resultant board. We then define a process that rearranges a sequence of earthquakes without changing the final board state and for a given board will always produce the same sequence.\\

@@

\begin{definition}
We say that an earthquake $E$ is valid if the node it targets has at least $4$ chips on it. 
We say that a sequence of earthquakes $E_1, E_2, \ldots E_n$ is a valid sequence of earthquakes if each earthquake is valid when applied one after another. 
\end{definition}

@@

We prove this by contradiction. Assume $E_2, E_1$ is an invalid sequence, that is $E_2 b(s_1)<4$. Since $E_1$ is a valid earthquake when applied directly to $b$, we know $b(s_1) \geq 4 $. 
Therefore we must have $b(s_1)<8$ and $s_2=s_1$. But then $E_1 b(s_1)<4$ and so $E_1, E_2$ would not be a valid sequence of earthquakes. This contradicts one of our hypotheses, and so $E_2, E_1$ is a valid sequence.
